% !TEX root = SystemTemplate.tex


\chapter{Project Overview}







\section{Team Members and Roles}
\hspace{5 mm}\underline{Autonomy}


Alex Muchow, Computer Science


Devin Kroeber, Electrical Engineering
\vspace{5 mm}


\underline{Moonrockers System}


Daniel Hodges, Mechanical Engineering

q
Samiel Hill, Mechanical Engineering


Jacob Green, Mechanical Engineering

\vspace{5 mm}
\underline{Icy Regolith}


Erik Figuracion, Mechanical Engineering


Mathew Gordon, Mechanical Engineering


Jonathan Stelzle, Mechanical Engineering



\section{Project  Management Approach}
For this project we will be managing through the Agile methodology. The length of each sprint will be two weeks long, and there will be a week in between for review and a report. The product backlog is currently in trello, but as there has been a lot of overhead work, the backlog remains as it originally stood. Trello will be used to update progress on each backlog item, and to address items being done during each sprint., as well as bug tickets.

\section{Phase  Overview}

	\vspace{\baselineskip}
	\textbf{Phase 1: 0.1}

	\begin{itemize}
	\item AR Tag designed
	\item ASUS Xtion location relative to AR tag
	\item Find a location to mount the camera sensor on the robot.
	\end{itemize}


	\vspace{\baselineskip}
	\vspace{\baselineskip}
	\vspace{\baselineskip}
	
	\newpage
	\textbf{Phase 2: 0.5}

	\begin{itemize}
	\item Robot able to center itself at the AR tag from any start location and orientation
	\item Find a way to mount the AR tag at the dump station
	\end{itemize}
	

	\vspace{\baselineskip}
	\textbf{Phase 3: 1.0}

	\begin{itemize}
	\item Robot successfully able to travel the distance from the dump station, over the obstacle course to the mining site, and travel back.
	\item Robot able to perform a mining routing
	\item Robot able to performing dumping at the AR tagged dumping station after navigating back
	\end{itemize}
	
	\vspace{\baselineskip}
	\textbf{Phase 4: 1.1}
	
	\begin{itemize}
	\item Manual override

	
	\end{itemize}
	\vspace{\baselineskip}


\section{Terminology and Acronyms}
\hspace{ 5mm}Regolith - Black Point-1(BP-1), or simulant for mars soil.

Icy Regolith - Simulant for larger pieces of martian soil, in our competition it is gravel.


NRMC - NASA Robotic Mining Competition.


ROS - Robot Operating System
